---
title: "Activities"
author: "Gloria"
date: "2022-12-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(dslabs)
ds_theme_set()
```

Load the data **gapminder**


**Explore the Data**

**1** Create a dataset from name **tidy_datasa** ("Botswana","Namibia","Angola","South Africa","Lesotho"). Use the filter and select function. ANd the head function.

```{r}

```

*** 2 Use ggplot to visualise your new data using (year, fertility, gdp, color = country)
 
```{r, warning=FALSE}
tidy_datasa %>% ggplot(aes(year, fertility, gdp, color = country)) +
              geom_point()
```
  
Let's explore


**3** Explore fertility across South Africa and Zimbabwe and name it `tidy_dsz`

```{r}


```
**4** Visualise the `tidy_dsz`

```{r, warning=FALSE}

```
**5** Use the Factorshiny function perform pca on the gapminder dataset dealing with the missing value. Motivate on the option selected to deal with missing value. 

```{r}


```